---
title: "Reform Project"
format: html
---
import the data and use janitor to clean names

```{r}
library(tidyverse)
library(readxl)
library(sandwich)
library(tseries)
library(tidyverse)
library(lubridate)
library(strucchange)
library(stargazer)
library(lavaan)
library(readr)
# Load time_series_GB_20040101_0000_20260422_0807 data
time_series_GB_20040101_0000_20260422_0807 <- read_csv("c:/Users/User/Downloads/time_series_GB_20040101-0000_20260422-0807.csv")
data_clean <- time_series_GB_20040101_0000_20260422_0807 %>%
  mutate(Time = ymd(Time))
data_clean = janitor::clean_names(data_clean)
data_clean$reform_uk = time_series_GB_20040101_0000_20260422_0807$`Reform UK`+time_series_GB_20040101_0000_20260422_0807$`UK Independence Party`
```
do a preliminary structural break  check on the immigration time series, we are going to be using pre defined dates though
```{r}
summary(strucchange::breakpoints(data_clean$immigration~1))
```
define break dummies using known immigration related topics such as brexit referendum
```{r}
data_clean <- data_clean %>% 
  mutate(breakdBpl = ifelse(time > as.Date("2019-04-01"), 1, 0), # Reform UK founded small boatscrisis# 
         breakpukip= ifelse(time>as.Date("2015-05-01"),1,0),    #Brexit #
         breakpukipl= ifelse(time>as.Date("2012-01-01"),1,0))  # Hostile Enviroment Policy# 
```
pre define immigration and inflation break coefs

```{r}
data_clean = data_clean %>% mutate(Refbreakim = immigration*breakdBpl,
Brexitbreakim = immigration*breakpukip,
Hostilebreakim = immigration*breakpukipl)
data_clean = data_clean %>% mutate(Refbreakinf = inflation*breakdBpl,
Brexitbreakinf = inflation*breakpukip,
Hostilebreakinf = inflation*breakpukipl)
```
define simple independent ols models

```{r}
breakmodel1im = lm(reform_uk~time+breakdBpl+breakpukip+breakpukipl+immigration+Refbreakim+Brexitbreakim+Hostilebreakim,data=data_clean)
breakmodel2im = lm(conservative_party~time+breakdBpl+breakpukip+breakpukipl+immigration+Refbreakim+Brexitbreakim+Hostilebreakim,data=data_clean)
breakmodel3im = lm(labour_party~time+breakdBpl+breakpukip+breakpukipl+immigration+Refbreakim+Brexitbreakim+Hostilebreakim,data=data_clean)
breakmodel4im = lm(liberal_democrats~time+breakdBpl+breakpukip+breakpukipl+immigration+Refbreakim+Brexitbreakim+Hostilebreakim,data=data_clean)
```
define a Seemingly Unrelated Regressions model structure

```{r}
sur_model_imm = '
#Outcome Regressions with breakpoints#

reform_uk~time+breakdBpl+breakpukip+breakpukipl+ b1r*immigration + b2r*Refbreakim + b3r*Brexitbreakim + b4r*Hostilebreakim
conservative_party~time+breakdBpl+breakpukip+breakpukipl + b1c*immigration + b2c*Refbreakim + b3c*Brexitbreakim + b4c*Hostilebreakim
labour_party~time+breakdBpl+breakpukip+breakpukipl + b1l*immigration + b2l*Refbreakim + b3l*Brexitbreakim+ b4l*Hostilebreakim
liberal_democrats~time+breakdBpl+breakpukip+breakpukipl + b1d*immigration + b2d*Refbreakim + b3d*Brexitbreakim + b4d*Hostilebreakim

#The Covariance Structure of the Seemingly Unrelated Regressions#

reform_uk~~conservative_party+labour_party+liberal_democrats
conservative_party~~labour_party+liberal_democrats
labour_party~~liberal_democrats

#Contrasts#
diff_ref_con := (b2r+b3r+b4r)-(b2c+b3c+b4c) #How much larger are slopes after breaks between Reform and Conservatives 
diff_con_lab := (b2c+b3c+b4c)-(b2l+b3l+b4l) # How much larger are slopes between Conservatives and Labour
diff_lab_lib := (b2l+b3l+b4l)-(b2d+b3d+b4d) # Between Labour and Lib Dem 
diff_con_lib := (b2c+b3c+b4c)-(b2d+b3d+b4d) # Between Conservatives and Lib dems 
diff_ref_main := ((b2r+b3r+b4r)-(b2c+b3c+b4c))-(((b2c+b3c+b4c)-(b2l+b3l+b4l))) # How different is the gap between reform and conservatives compared to conservatives and labour
'
```

fit a SUR


```{r}
set.seed(123)
fitsurimm = sem(sur_model_imm,data=data_clean,se="bootstrap",ncpus=12,bootstrap=2000,parallel="snow")
summary(fitsurimm,ci=TRUE)
```